
\begin{thebibliography}{00}


\bibitem{chen2007secret}
Chang-Chu Chen and Chin-Chen Chang.
\newblock Secret image sharing using quadratic residues.
\newblock In {\em Intelligent Information Hiding and Multimedia Signal Processing, 2007.}, volume~1, pages 515--518. IEEE, 2007.

\bibitem{CHI}
\newblock CTS Clearing House Interface – Specification, NCR Corporation and RBI/NPCI, 24th August, 2010

\bibitem{visualchen2013}
Wei-Kuei Chen and Hao-Kuan Tso.
\newblock Visual sharing protection method for medical images.
\newblock {\em Journal of medical systems}, 37(1):1--8, 2013.

\bibitem{lossless}
Binu~V. P and A.~Sreekumar.
\newblock Lossless secret image sharing schemes.
\newblock {\em International Journal of Computational Intelligence and
  Information Security}, 2013.

\bibitem{rbi}
RBI.
\newblock {\em RBI CTS}.
\newblock http://www.rbi.org.in.

\bibitem{shamir1979share}
Adi Shamir.
\newblock How to share a secret.
\newblock {\em Communications of the ACM}, 22(11):612--613, 1979.

\bibitem{sis}
Thien, Chih-Ching, and Ja-Chen Lin 
\newblock Secret image sharing.
\newblock {\em Computers and Graphics 26.5 }, 
pages 765-770, 2002.

\bibitem{boolean}
Chen, Tzung-Her, and Chang-Sian Wu
\newblock Efficient multi-secret image sharing based on Boolean operations.
\newblock {\em Signal Processing 91.1  }, 
pages 90-97,2011.

\bibitem{patent}
Calin A. Sandru, 125 Neptune Drive, Suite 606, North York (CA), M6A 1X3
\newblock Apparatus and method for enhancing the security of negotiable documents.
\newblock Patent No.:US 6,233,340 B1 , Date of Patent:May 15,2001
\bibitem{chequeprocessing}
R. Jayadevan, S. R. Kolhe, P. M. Patil, U. Pal
\newblock "Automatic processing of handwritten bank cheque images:
a survey" 
\newblock {International Journal on Document Analysis and Recognition (IJDAR) 15.4 (2012): 267-296}.
\bibitem{cheat2013}
Chen, Yu-Chi, Du-Shiau Tsai, and Gwoboa Horng. 
\newblock "Visual secret sharing with cheating prevention revisited." 

\end{thebibliography}